Precision calculations for cosmic shear

### 2017-02-09 cfhtlens.tex
added ExtL2FlHyb prelim. Sigma_8

  \begin{tabular}{lccc} \hline
  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ & Comment \\ \hline
  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Depreciated \\
  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
  ExtL2FlHyb & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Best flat-sky approximation \\
  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
  \end{tabular}

>>>>

  \begin{tabular}{lccc} \hline
  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ & Comment \\ \hline
  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Depreciated \\
  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.749^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
  \end{tabular}
